---
title: "Keenan-Early-Erin-ADAHomework-01"
author: "Erin Keenan Early"
date: "February 8, 2019"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Homework 1

## Challenge 1: Gettysburg Address

```{r}
abe<-c("Four score and seven years ago our fathers brought forth on this continent, a new nation, conceived in Liberty, and dedicated to the proposition that all men are created equal.")
abe
```

```{r}
library(stringr)
```

```{r}
abe_split<-str_split(abe, " ", simplify=TRUE)
abe_split
```

```{r}
abe3<-abe_split[seq(from=1, to=30, by =3)]
abe3
```

## Challenge 2: M Matrix

```{r}
m<-matrix(data = 1:80,nrow = 8, ncol = 10, byrow = FALSE)
m
```

Given the matrix, **m**, above, extract the 2nd, 3rd, and 6th columns and assign them to the variable **x**

```{r}
x<-m[,c(2,3,6)]
x
```

Given the matrix, **m**, above, extract the 6th to 8th row and assign them to the variable **x**

```{r}
x<-m[6:8,]
x
```

Given the matrix, **m**, above, extract the elements from row 2 column 2, to row 6 column 9 and assign them to the variable **x**

```{r}
x<-m[2:6,2:9]
x
```

## Challenge 3: Array

Construct a 4-dimensional, 400 element array (5x5x4x4) named **a** consisting of the numbers 400 to 1 (i.e., a descending series).

```{r}
a<-array(data=400:1, dim = c(5,5,4,4))
a
```

Given this matrix, what would the following return?

```{r}
a[1,1,1,2]
```
This returns the entry from the first row, first column in ,,1,2

```{r}
a[2,3,2,]
```
This returns the entry from the second row, third column in all 2nd "levels"

```{r}
a[1:5,1:5,3,3]
```
This returns the entries in rows 1 through 5 and columns 1 through 5 in ,,3,3,

## Challenge 4: Phylogeny

Create a **list** representing the (simplified) primate taxonomy.

```{r}
Order<-c("Primates")
Suborder<- c("Haplorhini", "Strepsirhini")
Infraorder <- c("Anthropoidea", "Tarsoidea", "Lorisoidea", "Lemuroidea")
Parvorder <- c("Platyrhini", "Catarrhini")
Family<- c("Cebidae", "Atelidae", "Pitheciidae", "Cercopithecidae", "Hylobatidae", "Hominidae", "Tarsiidae", "Lorisidae", "Galagidae", "Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae", "Daubentoniidae")
```

```{r}
Phylogeny<-list(Order,Suborder,Infraorder,Parvorder,Family)
Phylogeny
```
```{r}
Phylogeny[1]
Phylogeny[[2]][1]
Phylogeny[[3]][1]
Phylogeny[[4]][1]
Phylogeny[[5]][1:3]
Phylogeny[[4]][2]
Phylogeny[[5]][4:6]
Phylogeny[[3]][2]
Phylogeny[[5]][7]
Phylogeny[[2]][2]
Phylogeny[[3]][3]
Phylogeny[[5]][8:9]
Phylogeny[[3]][4]
Phylogeny[[5]][10:14]
```

## Challenge 5: 5x3 Matrix

Store the following numbers as a 5x3 matrix: 3,0,1,23,1,2,33,1,1,42,0,1,41,0,2. Be sure to fill the matrix **ROWWISE**

```{r}
matrix<-matrix(data = c(3, 0, 1, 23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2), nrow=5, ncol=3, byrow=TRUE)
matrix
```

Then do the following: 
Coerce the matrix to a data frame

```{r}
df<-data.frame(matrix)
df
```

As a data frame, coerce the second column to be *logical-valued* (Boolean)

```{r}
str(df)
```

```{r}
as.logical(df[[2]])
```


As a data frame, coerce the third column to be *factor-valued*

```{r}
as.factor(df[[3]])
```



